---
title: "Lab 06 - Projection of Bipartite Graphs"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    df_print: paged
    theme: flatly
    highlight: haddock
    toc: yes
    toc_float: yes
    code_fold: show
    self_contained: true
---

```{r setup, include = FALSE}

# Do not adjust these settings
# as they are here to set up 
# a few things for you.

knitr::opts_chunk$set( echo = TRUE,
                       eval = TRUE,
                      message = FALSE, 
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 6 )

```

```{r load_packages}

# load the packages you need
library( SNACpack )
library( network )
library( sna )

```

<br>

# Getting Started

## Setup

```{r}

# clear the workspace
rm( list = ls() )

```

<br>

## Part I: A Terrorism Network

### 1. Create an object of class `matrix` from the `baad_net` network. Use the `as.sociomatrix()` function in the `network` package to do so. ( **NOTE: DO NOT PRINT OUT THE MATRIX**).

```{r}

# Your code here

```

<br>

### 2. Create the unipartite graph that represents the *person* matrix.

```{r}

# Your code here

```

<br>

### 3. Create the unipartite graph that represents the *group* matrix.

```{r}

# Your code here

```

<br>

### 4. Plot all three networks. Use the `edge_rescale()` and `edge_shade()` functions in the `SNACpack` package to use the edge weights in the plots for each projected graph.

```{r}

# Your code here

```

<br>

### 5. Create an object of class `network` using the `as.network()` function. Pay attention to the correct usage of the `directed=` argument.

```{r}

# Your code here

```

<br>

### 6. Calculate the degree, closeness, and betweenness centrality scores for each actor. Feel free to use the `degree()`, `closeness()`, and `betweenness()` functions from the `sna` package.

```{r}

# Your code here

```

<br>

### 7. Calculate the mean degree, closeness, and betweenness centrality scores.

```{r}

# Your code here

```

<br>

### 8. Calculate the graph centralization scores for degree, closeness, and betweenness centrality.  

```{r}

# Your code here

```

<br>

### 9. Be sure to use the `vertex_rescale()` function to aid with the visualization.

```{r}

# Your code here

```

<br>

----

## Part II: A Kidnapping Network

### 1. Create an object of class `matrix` from the `philippine_kidnappings_net` network. Use the `as.sociomatrix()` function in the `network` package to do so. ( **NOTE: DO NOT PRINT OUT THE MATRIX**).

```{r}

# Your code here

```

<br>

<br>

### 2. Create the unipartite graph that represents the *person* matrix.

```{r}

# Your code here

```

<br>

### 3. Create the unipartite graph that represents the *group* matrix.

```{r}

# Your code here

```

<br>

### 4. Plot all three networks. Use the `edge_rescale()` and `edge_shade()` functions in the `SNACpack` package to use the edge weights in the plots for each projected graph.

```{r}

# Your code here

```

<br>

### 5. Create an object of class `network` using the `as.network()` function. Pay attention to the correct usage of the `directed=` argument.

```{r}

# Your code here

```

<br>

### 6. Calculate the degree, closeness, and betweenness centrality scores for each actor. Feel free to use the `degree()`, `closeness()`, and `betweenness()` functions from the `sna` package.

```{r}

# Your code here

```

<br>

### 7. Calculate the mean degree, closeness, and betweenness centrality scores.

```{r}

# Your code here

```

<br>

### 8. Calculate the graph centralization scores for degree, closeness, and betweenness centrality.  

```{r}

# Your code here

```

<br>

### 9. Be sure to use the `vertex_rescale()` function to aid with the visualization.

```{r}

# Your code here

```

<br>

----

## Part III: Your Network

For this part of the lab, I would like you use the bipartite network you created in [Lab 5](../labs/lab-05-instructions.html). 

For the bipartite network you created, repeat steps 1-4 from *Part I*.
For the *person* matrix you created in step 2, repeat steps 5-9 from *Part I*.