---
title: "Lab 03 - Degree Centrality"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    df_print: paged
    theme: flatly
    highlight: haddock
    toc: yes
    toc_float: yes
    code_fold: show
    self_contained: true
---

```{r setup, include = FALSE}

# Do not adjust these settings
# as they are here to set up 
# a few things for you.

knitr::opts_chunk$set( echo = TRUE,
                       eval = TRUE,
                      message = FALSE, 
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 6)

```

<br>

```{r load_packages}

# make sure you have installed the SNACpack package
# be sure to review the Getting Started with R chapter in
# the Social Network Analysis for Crime Analysts using R textbook
# if you have questions about how to install SNACpack
#
# note that you cannot knit with an install.packages() function
# called in your RMD file. You only have to install packages
# once, then they are loaded using the library() function.

# load the packages you need
library( SNACpack )
library( network )
library( sna )

```

<br>

# Getting Started

## Setup

```{r clear_workspace}

# clear the workspace
rm( list = ls() )

```

<br>

## Part I: Working with an Undirected Network

<br>

### 1. Plot the network using this command: `gplot( drug_net )`.

```{r}

# Your code here

```

<br>

### 2. How could you modify this plot to improve interpretability for a lay audience? Make at least <u>three changes</u> using the arguments in `gplot()`. Be sure to pay attention to the type of network it is and how best to represent the information in the network.

```{r}

# Your code here

```

<br>

### 3. Calculate the degree centrality score for each actor using the `rowSums()` function. 

```{r}

# Your code here

```

<br>

### 4. Plot the network using the `gplot()` function where nodes are sized by their degree centrality score (be sure to use the `vertex_rescale()` function to aid with correct sizing).

```{r}

# Your code here

```

<br>

### 5. Calculate the standardized degree centrality score using the equation from the readings for this week.

```{r}

# standardized score is deg / g-1 where g is the number of nodes.

# add your code here

```
  
<br>

### 6. Calculate the mean degree centrality score.

```{r}

# Your code here

```
  
<br>

### 7. Calculate the graph centralization score for degree centrality using the `centralization()` function in the `sna` package. 
  
```{r}

# Your code here

```
  
<br>

----

## Part II: Working with a Directed Network

<br>

### 1. Plot the network using this command: `gplot( heroin_dealing_net )`.

```{r}

# Your code here

```

<br>

### 2. How could you modify this plot to improve interpretability for a lay audience? Make at least <u>three changes</u> using the arguments in `gplot()`. Be sure to pay attention to the type of network it is and how best to represent the information in the network.

```{r}

# Your code here

```

<br>

### 3. Calculate the indegree and outdegree centrality scores for each actor using the `rowSums()` and `colSums()` functions.

```{r}

# Your code here

```

### 4. Plot the network using the `gplot()` function where nodes are sized by their <u>indegree</u> centrality score (be sure to use the `vertex_rescale()` function to aid with correct sizing).

```{r}

# Your code here

```

<br>

### 5. Plot the network using the `gplot()` function where nodes are sized by their <u>outdegree</u> centrality score (be sure to use the `vertex_rescale()` function to aid with correct sizing).

```{r}

# Your code here

```

<br>

### 6. Calculate the standardized indegree and outdegree centrality scores using the equation from the readings for this week. 

```{r}

# Your code here

```

<br>

### 7. Calculate the mean indegree and outdegree centrality scores.

```{r}

# Your code here

```

<br>

### 8. Calculate the graph centralization score for indegree and outdegree centrality using the `centralization()` function in the `sna` package. 

```{r}

# Your code here

```

<br>

----

## Part III: Your Networks

*Add your code setup here according to the instructions above, then DELETE THIS STATEMENT*
