---
title: "Lab 02 - Network Visualization"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    df_print: paged
    theme: flatly
    highlight: haddock
    toc: yes
    toc_float: yes
    code_fold: show
    self_contained: true
---

```{r load_packages}
# make sure these are installed on your machine before knitting
# install.packages( "network" )
# install.packages( "sna" )
#
# Note that you cannot knit with an install.packages() function
# called in your RMD file. You only have to install packages
# once, then they are loaded using the library() function.

library( network )
library( sna )

```

<br>

As indicated in the instructions, for *each* network you created, do the following:  

1. Create an adjacency matrix of the network using the `matrix()` function.
1. Create an object of class `network`. 
1. Plot the network using the `gplot()` function. Modify the plot using at least three arguments in the `gplot()` function.  
1. Calculate the density of the network.

As a refresher, review the example below.

<br>

## Example: 

Create your network, use the `matrix()` function:

<br>

```{r create-example, echo = TRUE, eval = TRUE}

# created a directed matrix
mat_d <- matrix(
  c(0,1,0,0,0,1,0,1,0,0,0,1,0,1,1,0,0,1,0,1,0,0,1,1,0),
  nrow=5,
  byrow=TRUE
  )

# attach row names
rownames( mat_d ) <- c( "Jen","Tom","Bob","Leaf","Jim" )

# attach column names
colnames( mat_d ) <- c( "Jen","Tom","Bob","Leaf","Jim" )

# print out the object
mat_d

```

<br>

Create an object of class `network` using the `as.network()` function. 

```{r coerce-example, echo =  TRUE, eval = TRUE}

# coerce the matrix object
net_d <- as.network( 
  mat_d,
  directed = TRUE # set this to false for an directed network; FALSE for an undirected network
  )

# print the object to see the properties
net_d

```

<br>

Finally, let's plot the networks using the `gplot()` function. Note that we can use either the object `mat_d` which is of class `matrix` or the object `net_d` which is of class `network`.

```{r create-undirected-plot, echo = TRUE, eval = TRUE}

# produce the plot
gplot(
  mat_d,                          # this is the network to plot
  gmode = "graph",                # let it know it is undirected    
  vertex.col = "lightblue",       # color the nodes
  vertex.cex = 1.2,               # size of the nodes (bigger number is bigger nodes)
  edge.col = "grey80",            # color the ties
  edge.lwd = 1.2,                 # the width of the ties (bigger is wider)
  main = "Plot of undirected net" # add a title
)

```

<br>

```{r create-directed-plot, echo = TRUE, eval = TRUE}

# produce the plot
gplot(
  mat_d,                          # this is the network to plot
  vertex.col = "firebrick",       # color the nodes
  vertex.cex = 1.2,               # size of the nodes (bigger number is bigger nodes)
  edge.col = "grey80",            # color the ties
  edge.lwd = 1.2,                 # the width of the ties (bigger is wider)
  main = "Plot of a directed net" # add a title
)

```

<br>

These were some examples to help you get going. Feel free to use them to aid in working through the lab. But, I encourage you to take the time to tinker with the different options in the `gplot()` function.

```{r clear-workspace, echo = TRUE, eval = TRUE}

# clear the workspace before you start working on your sections

rm( list = ls() )

```

----

# First Network

## Step 1

Create an adjacency matrix of the network using the `matrix()` function.

```{r}

# Your code here

```

<br>

## Step 2

Create an object of class `network`. 

```{r}

# Your code here

```

<br>

## Step 3

Plot the network using the `gplot()` function. Modify the plot using at least three arguments in the `gplot()` function.    

```{r}

# Your code here

```

<br>

## Step 4

Calculate the density of the network.

```{r}

# Your code here

```

<br>

----

# Second Network

## Step 1

Create an adjacency matrix of the network using the `matrix()` function.

```{r}

# Your code here

```

<br>

## Step 2

Create an object of class `network`. 

```{r}

# Your code here

```

<br>

## Step 3

Plot the network using the `gplot()` function. Modify the plot using at least three arguments in the `gplot()` function.    

```{r}

# Your code here

```

<br>

## Step 4

Calculate the density of the network.

```{r}

# Your code here

```
