---
title: "Lab 05 - Bipartite Graphs and Two-Mode Networks"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    df_print: paged
    theme: flatly
    highlight: haddock
    toc: yes
    toc_float: yes
    code_fold: show
    self_contained: true
---

```{r setup, include = FALSE}

# Do not adjust these settings
# as they are here to set up 
# a few things for you.

knitr::opts_chunk$set( echo = TRUE,
                       eval = TRUE,
                      message = FALSE, 
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 6 )

```

<br>


```{r load_packages}

# load the packages you need
library( SNACpack )
library( network )
library( sna )

```

<br>

# Getting Started

## Setup

```{r}

# clear the workspace
rm( list = ls() )

```

<br>

## Part I: A Terrorism Network

<br>

### 1. Plot the network using the `gplot()` function.

```{r}

# Your code here

```

<br>

### 2. Calculate the density of the network.

```{r}

# Your code here

```

### 3. Calculate the degree centrality scores for each set of nodes using the `rowSums()` and `colSums()` functions.  

```{r}

# Your code here

```

<br>

### 4. Calculate the mean degree centrality scores.

```{r}

# Your code here

```

<br>

### 5. Calculate the standardized degree centrality scores for each set of nodes.  

```{r}

# Your code here

```

<br>

### 6. Calculate the mean standardized degree centrality score.  

```{r}

# Your code here

```

<br>

### 12. Plot the network using the standardized degree centrality scores (be sure to use the `vertex_rescale()` function to aid with rescaling). 

```{r}

# Your code here

```

<br>

----

## Part II: A Kidnapping Network

<br>

### 1. Plot the network using the `gplot()` function.

```{r}

# Your code here

```

<br>

### 2. Calculate the density of the network.

```{r}

# Your code here

```

### 3. Calculate the degree centrality scores for each set of nodes using the `rowSums()` and `colSums()` functions.  

```{r}

# Your code here

```

<br>

### 4. Calculate the mean degree centrality scores.

```{r}

# Your code here

```

<br>

### 5. Calculate the standardized degree centrality scores for each set of nodes.  

```{r}

# Your code here

```

<br>

### 6. Calculate the mean standardized degree centrality score.  

```{r}

# Your code here

```

<br>

### 12. Plot the network using the standardized degree centrality scores (be sure to use the `vertex_rescale()` function to aid with rescaling). 

```{r}

# Your code here

```

<br>

----

## Part III: Your Network

### A. Create an adjacency matrix of the network using the `matrix()` function.

```{r}

# Your code here

```

<br>

### B. Create an object of class `network`. 

```{r}

# Your code here

```

<br>

*Add your code setup here according to the instructions above, then DELETE THIS STATEMENT*