---
title: "Lab 04 - CLoseness/Betweenness Centrality"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    df_print: paged
    theme: flatly
    highlight: haddock
    toc: yes
    toc_float: yes
    code_fold: show
    self_contained: true
---

```{r setup, include = FALSE}

# Do not adjust these settings
# as they are here to set up 
# a few things for you.

knitr::opts_chunk$set( echo = TRUE,
                       eval = TRUE,
                      message = FALSE, 
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 6 )

```

<br>

```{r load_packages}

# load the packages you need
library( SNACpack )
library( network )
library( sna )

```

<br>

# Getting Started

## Setup

```{r clear_workspace}

# clear the workspace
rm( list = ls() )

```

<br>

## Part I: Working with an Undirected Network

<br>

### 1. Calculate the degree, closeness, and betweenness centrality scores for each actor. Feel free to use the `degree()`, `closeness()`, and `betweenness()` functions from the `sna` package. For closeness, pay attention to whether the graph is disconnected and how to deal with calculating closesness centrality on such graphs.


```{r}

# Your code here

```

<br>

### 2. Calculate the mean closeness centrality score and the mean betweenness centrality score.

```{r}

# Your code here

```

<br>

### 3. Calculate the graph centralization scores for degree, closeness, and betweenness centrality using the `centralization` function in the `sna` package. Again, for closeness, pay attention to the structure of the graph and how this influences your calculation.

```{r}

# Your code here

```

<br>

### 4. Plot the network three times using the `gplot()` function where each plot sizes the nodes by the centrality score (i.e., a plot for degree centrality, a plot for closeness centrality, and a plot for betweenness centrality).

```{r}

# Your code here

```

<br>

----

## Part II: Working with a Directed Network

<br>

### 1. Calculate the indegree, outdegree, closeness, and betweenness centrality scores for each actor. Feel free to use the `degree()`, `closeness()`, and `betweenness()` functions from the `sna` package.

```{r}

# Your code here

```

<br>

### 2. Calculate the mean closeness centrality score and the mean betweenness centrality score.

```{r}

# Your code here

```

<br>

### 3. Calculate the graph centralization scores for indegree, outdegree, closeness, and betweenness centrality using the `centralization` function in the `sna` package.  

```{r}

# Your code here

```

<br>

### 4. Plot the network four times using the `gplot()` function where each plot sizes the nodes by the centrality score (i.e., a plot for indegree centrality, a plot for outdegree centrality, a plot for closeness centrality, and a plot for betweenness centrality).

```{r}

# Your code here

```

<br>

----

## Part III: Your Networks

*Add your code setup here according to the instructions above, then DELETE THIS STATEMENT*
